### 2012-10-24 inst/examples/reed-example.Rmd
Different choice of hyperparameters
Varying the hyperparameters has little direct impact around the data,
though with lower correlation lengths the influence of the prior
where there is no data becomes obvious.

```{r libraries}
require(pdgControl)
require(ggplot2)
```

@@

```{r}
obs <- data.frame(x=x[1:(T-1)],y=x[2:T])
X <- x_grid
library(nonparametricbayes)
gp <- gp_fit(obs, X, c(sigma_n=.05, l=10))
```

@@

```{r}
obs <- data.frame(x=x[1:(T-1)],y=x[2:T])
X <- x_grid
library(nonparametricbayes)
gp <- gp_fit(obs, X, c(sigma_n=.05, l=10))
```

@@

>>>>

```{r libraries}
require(pdgControl)
require(ggplot2)
opts_knit$set(upload.fun = socialR::flickr.url)
```

@@

```{r}
obs <- data.frame(x=x[1:(T-1)],y=x[2:T])
X <- x_grid
library(nonparametricbayes)
gp <- gp_fit(obs, X, c(sigma_n=1, l=1))
```

@@

```{r}
obs <- data.frame(x=x[1:(T-1)],y=x[2:T])
X <- x_grid
gp <- gp_fit(obs, X, c(sigma_n=1, l=1))
```

@@

## Further steps

* is the posterior GP capturing the process noise?
* Need to add optimization over hyperparameters
